Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-13 ms.tex
Fixing a couple of typos in the description of rb.

A galaxy model is fully specified by four parameters: $\Mbh$,
$\Gamma$, $r_b$, and $\beta$.  We compute models for three different
black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.  The
distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is
bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim
0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
We bracket these possibilities by considering models with $\Gamma=0.8$
and $\Gamma=0.1$.  Since our results are most sensitive to the
properties of the gas flow on radial scales $\ll r_b$, we fix $\beta =
2$ (a typical value). In any case, the flow inside $\rb$ is
insensitive the outer power law slope of the stellar density
profile. However, the presence of $\rb$ is necessary for to obtain a
converged steady state for some regions of our parameter space.  We
consider four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
and 400 pc. These choices are motivated by the observed break radii in
the \citet{LauerFaber+:2007a} sample. For the core galaxies
($\Gamma$<0.3) in this sample the break radius follows the scaling
relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
approximately one dex. Most the cusp ($\Gamma>0.5$) galaxies have
$\rb$ between 100 and 1000 pc, and there is not trend with
$\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
  significant effect on rs it may not be necessary to do runs. For
  instance for Mbh=$10^8$ Msun, gamma=0.8, and vw0=600 km/s the
  stagnation radius changes by only 8\%. So for cusp galaxies with
  vw0$\gsim$600 km/s and Mbh$\lsim 10^8$ Msun it seems like it is a
  safe bet to neglect the effect of the break radius on the
  solution. For low heating rates it my be difficult to converged
  solution for large values of rb=200 and 400 pc.}
% However, the presence of $\rb$ is necessary for to obtain a
% converged steady state for some regions of our parameter space. We
% adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core
% galaxy models we employ the scaling relation $\rb = $, motivated again
% by the \citet{LauerFaber+:2007a} sample. ({\bf BDM: fill in!}).
% Though simplistic, our results are not sensitive to our assumption
% about the value of $\rb$.

>>>>

A galaxy model is fully specified by four parameters: $\Mbh$,
$\Gamma$, $r_b$, and $\beta$.  We compute models for three different
black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.  The
distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is
bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim
0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
We bracket these possibilities by considering models with $\Gamma=0.8$
and $\Gamma=0.1$.  Since our results are most sensitive to the
properties of the gas flow on radial scales $\ll r_b$, we fix $\beta =
2$ (a typical value). In any case, the flow inside $\rb$ is
insensitive the outer power law slope of the stellar density
profile. However, the presence of $\rb$ is necessary for to obtain a
converged steady state for some regions of our parameter space.  We
consider four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
and 400 pc. These choices are motivated by the observed break radii in
the \citet{LauerFaber+:2007a} sample. For the core galaxies
($\Gamma \le$0.3) in this sample the break radius follows the scaling
relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
approximately one dex. Most the cusp ($\Gamma \ge0.5$) galaxies have
$\rb$ between 100 and 1000 pc, and there is not trend with
$\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
  significant effect on rs it may not be necessary to do runs. For
  instance for Mbh=$10^8$ Msun, gamma=0.8, and vw0=600 km/s the
  stagnation radius changes by only 8\%. So for cusp galaxies with
  vw0$\gsim$600 km/s and Mbh$\lsim 10^8$ Msun it seems like it is a
  safe bet to neglect the effect of the break radius on the
  solution. For low heating rates it my be difficult to converged
  solution for large values of rb=200 and 400 pc.}
% However, the presence of $\rb$ is necessary for to obtain a
% converged steady state for some regions of our parameter space. We
% adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core
% galaxy models we employ the scaling relation $\rb = $, motivated again
% by the \citet{LauerFaber+:2007a} sample. ({\bf BDM: fill in!}).
% Though simplistic, our results are not sensitive to our assumption
% about the value of $\rb$.
